---
title: 'Project 2: Modeling and Evaluation'
subtitle: 'GID: mmendiola3'
output:
  pdf_document: default
  html_document: default
---

# Data

We will use the same dataset as Project 1: [`movies_merged`](https://s3.amazonaws.com/content.udacity-data.com/courses/gt-cs6242/project/movies_merged).

# Objective

Your goal in this project is to build a linear regression model that can predict the `Gross` revenue earned by a movie based on other variables. You may use R packages to fit and evaluate a regression model (no need to implement regression yourself). Please stick to linear regression, however.

# Instructions

You should be familiar with using an [RMarkdown](http://rmarkdown.rstudio.com) Notebook by now. Remember that you have to open it in RStudio, and you can run code chunks by pressing *Cmd+Shift+Enter*.

Please complete the tasks below and submit this R Markdown file (as **pr2.Rmd**) containing all completed code chunks and written responses, as well as a PDF export of it (as **pr2.pdf**) which should include all of that plus output, plots and written responses for each task.

_Note that **Setup** and **Data Preprocessing** steps do not carry any points, however, they need to be completed as instructed in order to get meaningful results._

# Setup

Same as Project 1, load the dataset into memory:

```{r}
load('movies_merged')
```

This creates an object of the same name (`movies_merged`). For convenience, you can copy it to `df` and start using it:

```{r}
df = movies_merged
cat("Dataset has", dim(df)[1], "rows and", dim(df)[2], "columns", end="\n", file="")
colnames(df)
```

## Load R packages

Load any R packages that you will need to use. You can come back to this chunk, edit it and re-run to load any additional packages later.

```{r echo=FALSE}
library(ggplot2)
library(GGally)
library(mice)
library(reshape2)
library(caret)
library(mlbench)
library(randomForest)
library(dplyr)
library(qdap)
library(splitstackshape)
library(stringr)
library(leaps)
library(MASS)
```

If you are using any non-standard packages (ones that have not been discussed in class or explicitly allowed for this project), please mention them below. Include any special instructions if they cannot be installed using the regular `install.packages('<pkg name>')` command.

**Non-standard packages used**: None

# Data Preprocessing

Before we start building models, we should clean up the dataset and perform any preprocessing steps that may be necessary. Some of these steps can be copied in from your Project 1 solution. It may be helpful to print the dimensions of the resulting dataframe at each step.

## 1. Remove non-movie rows

```{r}
# TODO: Remove all rows from df that do not correspond to movies
df <- subset(df, Type == 'movie')
nrow(df)
```

## 2. Drop rows with missing `Gross` value

Since our goal is to model `Gross` revenue against other variables, rows that have missing `Gross` values are not useful to us.

```{r}
# TODO: Remove rows with missing Gross value
df <- subset(df, !is.na(Gross))
nrow(df)
```

## 3. Exclude movies released prior to 2000

Inflation and other global financial factors may affect the revenue earned by movies during certain periods of time. Taking that into account is out of scope for this project, so let's exclude all movies that were released prior to the year 2000 (you may use `Released`, `Date` or `Year` for this purpose).

```{r}
# TODO: Exclude movies released prior to 2000
df <- subset(df, Year >= 2000)
nrow(df)
```

## 4. Eliminate mismatched rows

_Note: You may compare the `Released` column (string representation of release date) with either `Year` or `Date` (numeric representation of the year) to find mismatches. The goal is to avoid removing more than 10% of the rows._

```{r}
# TODO: Remove mismatched rows
year_delta <- function(year_, date) {
  if (is.na(year_) || is.na(date)) {
    return(0)
  } else if (year_ == as.numeric(format(date, "%Y"))) {
    return(0)
  }
  date = as.Date(date)
  year_start = as.Date(ISOdate(year_, 1, 1))
  year_end = as.Date(ISOdate(year_, 12, 31))
  diff = min(abs(c(date - year_start, date - year_end)))
  return(diff)
}

df$DaysDiff = mapply(year_delta, df$Year, df$Released)

# Threshold of days between Release and Year
threshold = 90
df_dedupped <- subset(df, DaysDiff < threshold)
sprintf("percent of rows removed: %f", 100 * (1 - (nrow(df_dedupped) / nrow(df))))

# Commit changes to df
df_before_dedup <- cbind(df)
df <- df_dedupped
```

## 5. Drop `Domestic_Gross` column

`Domestic_Gross` is basically the amount of revenue a movie earned within the US. Understandably, it is very highly correlated with `Gross` and is in fact equal to it for movies that were not released globally. Hence, it should be removed for modeling purposes.

```{r}
# TODO: Exclude the `Domestic_Gross` column
df <- subset(df, select=-Domestic_Gross)
```

## 6. Process `Runtime` column

```{r}
# TODO: Replace df$Runtime with a numeric column containing the runtime in minutes
parseRuntime <- function(string) {
  parts = unlist(strsplit(string, ' '))
  if (length(parts) == 2) {
    return(as.numeric(parts[1]))
  } else if (length(parts) == 4) {
    return(as.numeric(parts[1]) * 60 + as.numeric(parts[3]))
  } else {
    return(NA)
  }
}

df$Runtime = sapply(df$Runtime, parseRuntime)
```

Perform any additional preprocessing steps that you find necessary, such as dealing with missing values or highly correlated columns (feel free to add more code chunks, markdown blocks and plots here as necessary).

```{r}
# TODO(optional): Additional preprocessing
# Generate month feature to replace Released
df$Month = as.numeric(format(df$Released, "%m"))

# Convert Metascore to num
df$Metascore <- as.numeric(df$Metascore)

# Remove featues with clearly no correlation with Gross
df <- subset(df, select=-c(Date, Released, Poster, imdbID, Type, tomatoImage, tomatoURL, BoxOffice, Website, Response, DaysDiff))

# Filter major outlier
df <- subset(df, Gross < 2e9)

# Remove features with high pairwise correlation values with remaining features
# Remove the feature with more NAs
# ggpairs(df[,c("tomatoMeter", "tomatoRating", "tomatoReviews", "tomatoFresh", "tomatoRotten", "tomatoUserMeter", "tomatoUserRating", "tomatoUserReviews", "imdbRating", "imdbVotes")])

# Remove features with more than 10% NAs
pMiss <- function(x){round(sum(is.na(x))/length(x)*100)}
mc <- apply(df, 2, pMiss)
columns_to_keep <- names(mc[mc < 10])
df <- subset(df, select=columns_to_keep)
df_numeric <- df[, sapply(df, is.numeric)]

# Remove high correlation features
cor_matrix <- cor(subset(df_numeric, select=-Gross), use='pairwise.complete.obs')
high_cor <- colnames(cor_matrix[, findCorrelation(cor_matrix, cutoff=0.75)])
df <- subset(df, select=-c(tomatoUserMeter, tomatoUserRating))

# Remove samples with NAs
df <- df[complete.cases(df), ]
df_numeric <- df[, sapply(df, is.numeric)]
```

_**Note**: Do NOT convert categorical variables (like `Genre`) into binary columns yet. You will do that later as part of a model improvement task._

## Final preprocessed dataset

Report the dimensions of the preprocessed dataset you will be using for modeling and evaluation, and print all the final column names. (Again, `Domestic_Gross` should not be in this list!)

```{r}
# TODO: Print the dimensions of the final preprocessed dataset and column names
print('DF dims:')
dim(df)

print('DF column names:')
names(df)
```

# Evaluation Strategy

In each of the tasks described in the next section, you will build a regression model. In order to compare their performance, use the following evaluation procedure every time:

1. Randomly divide the rows into two sets of sizes 5% and 95%.
2. Use the first set for training and the second for testing.
3. Compute the Root Mean Squared Error (RMSE) on the train and test sets.
4. Repeat the above data partition and model training and evaluation 10 times and average the RMSE results so the results stabilize.
5. Repeat the above steps for different proportions of train and test sizes: 10%-90%, 15%-85%, ..., 95%-5% (total 19 splits including the initial 5%-95%).
6. Generate a graph of the averaged train and test RMSE as a function of the train set size (%).

You can define a helper function that applies this procedure to a given model and reuse it.

```{r}

plot_sub_data <- function(df, title, data_type) {
  df <- melt(df, id.vars='train_size', measure.vars=c('train', 'test'))
  return(ggplot(df, aes(train_size, value, color=variable)) +
    geom_line() +
    geom_point() +
    ggtitle(title) +
    # scale_y_continuous(labels=function(x) format(x, digits=2), breaks=seq(signif(min(df$value), 2), signif(max(df$value), 2), length.out=8)) +
    labs(x='Train size (ratio of original data)', y=data_type))
}

evaluate_model_range('Gross~.', df_numeric, 'Gross')

split_data <- function(df, train_ratio=0.8) {
  train_indicies<- sample(1:nrow(df), floor(train_ratio * nrow(df)))
  return(list(train=df[train_indicies,], test=df[-train_indicies,]))
}

evaluate_model <- function(formula, df, train_ratio=0.8, y_label='Gross', trials=50) {
  result_train <- vector()
  result_test <- vector()

  for (i in 1:trials) {
    df_sample <- split_data(df, train_ratio)
    
    model <- lm(formula, df_sample$train)
    result_train <- c(result_train, sqrt(mean(model$residuals^2)))
    suppressWarnings(test_residuals <- df_sample$test[, y_label] - predict(model, df_sample$test))
    result_test <- c(result_test, sqrt(mean(test_residuals^2)))
  }
  return(list(
            train=mean(result_train),
            test=mean(result_test),
            train_sd=sd(result_train),
            test_sd=sd(result_test)
         ))
}

evaluate_model('Gross~.', df_numeric)

evaluate_model_range <- function(formula, df, y_label='Gross', trials=50) {
  rmse <- data.frame()
  for (i in seq(0.05, 0.95, 0.05)) {
    rmse <- rbind(rmse, c(evaluate_model(formula, df, i, y_label, trials), train_size=i))
  }
  return(list(rmse=rmse, plot=plot_sub_data(rmse, 'RMSE vs. Training size', 'RMSE')))
}

evaluate_model_change <- function(formula1, df1, formula2, df2) {
  r1 <- evaluate_model(formula1, df1, trials=1000)
  r2 <- evaluate_model(formula2, df2, trials=1000)
  return(list(
    # r1=r1,
    # r2=r2,
    # train_diff=r2$train - r1$train,
    # test_diff=r2$test - r1$test,
    train_upper_diff=(r2$train + r2$train_sd) - (r1$train + r1$train_sd),
    test_upper_diff=(r2$test + r2$test_sd) - (r1$test + r1$test_sd)
  ))
}

feature_selection <- function(df) {
  # Feature selection
  # define the control using a random forest selection function
  control <- rfeControl(functions=rfFuncs, method="cv", number=10)
  # run the RFE algorithm
  results <- rfe(subset(df_numeric, select=-Gross), df_numeric[, 'Gross'], sizes=ncol(df_numeric)-1, rfeControl=control)
  # summarize the results
  print(results)
  # list the chosen features
  predictors(results)
  # plot the results
  plot(results, type=c("g", "o"))
  return(results)
}

# d=data.frame(x=1:1000, y=1001:2000)
# a=evaluate_model_range('y~x', d, 'y')
```

# Tasks

Each of the following tasks is worth 20 points. Remember to build each model as specified, evaluate it using the strategy outlined above, and plot the training and test errors by training set size (%).

## 1. Numeric variables

Use linear regression to predict `Gross` based on all available _numeric_ variables.

```{r}
# TODO: Build & evaluate model 1 (numeric variables only)
df_numeric <- df[, sapply(df, is.numeric)]

print('Numeric columns:')
names(df_numeric)

result <- evaluate_model_range('Gross~.', df_numeric, 'Gross')
print(result$plot)
```

**Q**: List all the numeric variables you used.

**A**: "Year" "Runtime" "imdbRating" "imdbVotes" "tomatoUserReviews" "Budget" "Month"

## 2. Feature transformations

Try to improve the prediction quality from **Task 1** as much as possible by adding feature transformations of the numeric variables. Explore both numeric transformations such as power transforms and non-numeric transformations of the numeric variables like binning (e.g. `is_budget_greater_than_3M`).

### Setup functions
These help to evaluate numeric and non-numeric transformations

```{r}
# TODO: Build & evaluate model 2 (transformed numeric variables only)

df_nt <- cbind(df_numeric)

reg_transforms <- function(x, y) {
  return(list(
    linear = lm(y~x),
    log = lm(y~log(x+1)),
    quad = lm(y~I(x^2)),
    cubic = lm(y~I(x^3)),
    quartic = lm(y~I(x^4)),
    quintic = lm(y~I(x^5)),
    reciprocal = lm(y~1/(x+1))
  ))
}

get_r2 <- function(fit) {
  return(summary(fit)$r.squared)
}

get_rmse <- function(fit) {
  return(sqrt(mean(fit$residuals^2)))
}

get_cor <- function(fit) {
  return(as.vector(cor(fit$model[1], fit$model[2])))
}

eval_fit <- function(fit) {
  return(data.frame(r2=get_r2(fit), rmse=get_rmse(fit), cor=get_cor(fit)))
}

best_bins <- function(x, y) {
  fit <- lm(y ~ x)
  result <- list(r2=summary(fit)$r.squared, bins=0)
  for (i in 1:200) {
    b <- ntile(x, i)
    fit <- lm(y ~ b)
    r2 <- summary(fit)$r.squared
    if (r2 > result$r2) {
      result$r2 <- r2
      result$bins <- i
    }
  }
  return(result)
}
```

### Visualize features
```{r}
for (feature in setdiff(names(df_nt), 'Gross')) {
  print(plot(df_nt[,feature], df_nt$Gross, main=feature))
}
```


### Evaluate numeric transformations

```{r}
for (feature in setdiff(names(df_numeric), 'Gross')) {
  print(feature)
  fits <- reg_transforms(df_numeric[, feature], df_numeric$Gross)
  perf <- sapply(fits, eval_fit)
  print(perf)
}

```

```{r}
for (feature in setdiff(names(df_numeric), 'Gross')) {
  b <- best_bins(df_numeric[, feature], df_numeric$Gross)
  if (b$bins > 0) {
    print(cbind(b, name=feature))
  }
}
```

**Transform Year**
```{r}
df_nt <- cbind(df_numeric)
df_nt$Year_bin <- ntile(df_numeric$Year, 5)
evaluate_model_change('Gross~.', df_numeric, 'Gross~.', df_nt)
```

**Transform Runtime**
```{r}
df_nt <- cbind(df_numeric)
df_nt$Runtime_cubic <- df_nt$Runtime^3
evaluate_model_change('Gross~.', df_numeric, 'Gross~.', df_nt)
```
                     
**Transform imdbRating**
```{r}
eval_fit(lm(Gross ~ I(imdbRating^11), df_nt))
df_nt <- cbind(df_numeric)
df_nt$imdbRating_power <- df_nt$imdbRating^11
evaluate_model_change('Gross~.', df_numeric, 'Gross~.', df_nt)
```

**Transform tomatoUserReviews**
```{r}
df_nt <- cbind(df_numeric)
df_nt$tomatoUserReviews_bin <- ntile(df_numeric$tomatoUserReviews, 39)
evaluate_model_change('Gross~.', df_numeric, 'Gross~.', df_nt)
```

**Transform Month**
```{r}
df_nt <- cbind(df_numeric)
df_nt$Month_bin <- ntile(df_numeric$tomatoUserReviews, 6)
evaluate_model_change('Gross~.', df_numeric, 'Gross~.', df_nt)
```

### Transform all
```{r}
df_nt <- cbind(df_numeric)
df_nt$Year_bin <- ntile(df_numeric$Year, 5)
df_nt$Runtime_cubic <- df_nt$Runtime^3
df_nt$imdbRating_power <- df_nt$imdbRating^11
df_nt$tomatoUserReviews_bin <- ntile(df_numeric$tomatoUserReviews, 39)
df_nt$Month_bin <- ntile(df_numeric$tomatoUserReviews, 6)
evaluate_model_change('Gross~.', df_numeric, 'Gross~.', df_nt)
evaluate_model_range('Gross~.', df_nt)
```


**Q**: Explain which transformations you used and why you chose them.

**A**: 

Each feature was evaluted for a number of different numeric transforms:

    linear = lm(y~x),
    log = lm(y~log(x+1)),
    quad = lm(y~I(x^2)),
    cubic = lm(y~I(x^3)),
    quartic = lm(y~I(x^4)),
    quintic = lm(y~I(x^5)),
    reciprocal = lm(y~1/(x+1))
    
A model was built with each transformation and the resulting R^2, RMSE, and correlation coefficient was inspected.

Binning was also evaluated for each feature by splitting the data points into equal sized bins. Bin counts between 1 and 200 were tested and the bin count that resulted in the highest r^2 model was chosen.

For each feature, the model fit metrics were inspected before and after applying each of these transformations. Based on the results, the following feature transformations were done:

Year: Split into 5 equally sized bins.
Runtime: Tranformed into Runtime^3
imdbRating: Tranformed into imdbRating^11 (this one was strange, but was included because it did result in a significant metric improvement)
tomatoUserReviews: Split into 39 equally sized bins. This transformation made intuitive sense given the highly irregular distribution.
Month: Split into 6 equally sized bins.


## 3. Non-numeric variables

Write code that converts genre, actors, directors, and other categorical variables to columns that can be used for regression (e.g. binary columns as you did in Project 1). Also process variables such as awards into more useful columns (again, like you did in Project 1). Now use these converted columns only to build your next model.

```{r}
# TODO: Build & evaluate model 3 (converted non-numeric variables only)
df_cat <- df[, sapply(df, function(x) !is.numeric(x))]
df_cat$Gross <- df$Gross
df_cat <- subset(df_cat, select=-c(DVD, Title, tomatoConsensus, Plot))


factor_to_features <- function(df, feature, top=10) {
  df_factor <- subset(df, select=feature)
  df_features <- model.matrix(~., df_factor)
  sums <- colSums(df_features)
  top_features = names(sort(sums, decreasing = TRUE)[1:top])
  df_features <- subset(df_features, select=top_features)
  df <- cbind(df, df_features)
  df[c(feature, '(Intercept)')] = NULL
  return(df)
}

string_to_features <- function(df, feature, top=10) {
  df_sub <- subset(df, select=feature)
  df_sub <- cSplit_e(df_sub, feature, sep=',', mode='binary', type='character', fill=0, drop=TRUE)
  sums <- colSums(df_sub)
  top_features = names(sort(sums, decreasing = TRUE)[1:top])
  df <- cbind(df, subset(df_sub, select=top_features))
  df[c(feature, 'na')] = NULL
  return(df)
}

clean_writer_strings <- function(string_) {
  return(str_replace_all(string_, ' *\\([^\\)]*\\)', ''))
}

# Clean 'Writer'
df_cat$Writer <- sapply(df_cat$Writer, clean_writer_strings)

# 'Rated', 'Production'
for (feature in c('Rated', 'Production')) {
  df_cat <- factor_to_features(df_cat, feature)
}

# 'Genre', 'Director', 'Writer', 'Actors', 'Language', 'Country'
for (feature in c('Genre', 'Director', 'Writer', 'Actors', 'Language', 'Country')) {
  df_cat = string_to_features(df_cat, feature)
}
df_cat[c('Writer', 'na', 'Writer_N/A')] = NULL

# Awards
parse_awards <- function(msg, patterns) {
  if (is.na(msg)) {
    return(NA)
  }
  msg = tolower(msg)
  value = 0
  for (pattern in patterns) {
    m = str_match(msg, pattern)[1, 2]
    if (!is.na(m)) {
      value = value + as.integer(m)
    }
  }
  return(value)
}

awards_patterns = c('won (\\d+)', "(\\d+) win")
nomination_patterns = c('nominated for (\\d+)', "(\\d+) nomination")
df_cat$Wins = sapply(df_cat$Awards, parse_awards, pattern=awards_patterns)
df_cat$Nominations = sapply(df_cat$Awards, parse_awards, pattern=nomination_patterns)
df_cat['Awards'] = NULL
```

```{r}
r <- evaluate_model_range('Gross~.', df_cat)
print(r$plot)
```

**Q**: Explain which categorical variables you used, and how you encoded them into features.

**A**: 

I used the following features:

  'Rated', 'Production' 'Genre', 'Director', 'Writer', 'Actors', 'Language', 'Country' 'Awards'
  
Rated and Production were converted by taking the set of unique values and making each a seperate binary feature. These features were then reduced to the top ten most common.

The remaining features, besides Awards, were converted by parsing the string as comma seperated values and creating binary features from each of the unique extracted values. As before, only the top ten most common derived features were retained.

The Awards feature extraction uses regex parsing to pull out the number of wins and nominations. Wins and Nominations features replace Awards.


## 4. Numeric and categorical variables

Try to improve the prediction quality as much as possible by using both numeric and non-numeric variables from **Tasks 2 & 3**.

```{r}
# TODO: Build & evaluate model 4 (numeric & converted non-numeric variables)
df_all <- cbind(df_nt, subset(df_cat, select=-Gross))

r <- evaluate_model_range('Gross~.', df_all)
print(r$plot)

# evaluate_model_change('Gross~.', df_nt, 'Gross~.', df_all)

# Remove high correlation features
cor_matrix <- cor(subset(df_all, select=-Gross), use='pairwise.complete.obs')
high_cor <- findCorrelation(cor_matrix, cutoff=0.75)
print('High cor features:')
print(names(df_all[, high_cor]))
df_filtered <- df_all[, -c(high_cor)]
# df <- subset(df, select=-c(tomatoUserMeter, tomatoUserRating))
```

## 5. Additional features

Now try creating additional features such as interactions (e.g. `is_genre_comedy` x `is_budget_greater_than_3M`) or deeper analysis of complex variables (e.g. text analysis of full-text columns like `Plot`).

```{r}
# TODO: Build & evaluate model 5 (numeric, non-numeric and additional features)
evaluate_model_range('Gross~.^2', df_filtered, trials=10)
fit <- lm(Gross~.^2, df_filtered)
summary(fit)$r.squared

filter_columns <- function(df, column_names) {
  if (length(column_names) == 0) {
    return(df)
  } else {
    return(df[, -which(names(df) %in% column_names)])
  }
}

run_rfe <- function(x, y) {
  # subsets <- c(1:5, 10, 15, 20, 25)
       
  ctrl <- rfeControl(functions=lmFuncs)
  # ctrl <- rfeControl(functions = lmFuncs,
  #                    method = "repeatedcv",
  #                    repeats = 5,
  #                    verbose = FALSE)
  
  lmProfile <- rfe(x, y,
                   # sizes = subsets,
                   rfeControl = ctrl)
  return(lmProfile)
}

lmp_nt <- run_rfe(filter_columns(df_nt, c(n, 'Gross')), df_nt$Gross)
lmp_nt
print(lmp_nt)
plot(lmp_nt)
head(lmp_nt$resample)
pred_nt <- predictors(lmp_nt)
pred_nt
# x <- subset(df_cat_filtered, select=-Gross)
# x <- preProcess(x)
lmp_cat <- run_rfe(x, df_cat_filtered$Gross)


filter_high_cor <- function(df) {
  cor_matrix <- cor(subset(df, select=-Gross), use='pairwise.complete.obs')
  high_cor <- findCorrelation(cor_matrix, cutoff=0.75)
  return(df[, -c(high_cor)])
}

filter_near_zero_var <- function(df) {
  near_zero_var_columns <- names(df)[nearZeroVar(df)]
  return(filter_columns(df, near_zero_var_columns))
}

df_cat_filtered <- filter_columns(df_cat, names(df_cat)[nearZeroVar(df_cat)])
df_cat_filtered <- filter_high_cor(df_cat_filtered)
x <- subset(df_cat_filtered, select=-Gross) 

fit <- lm(Gross~., df_cat_filtered)
influence(fit)

leapSet <- 
leapSet <- leaps(x, df_cat_filtered$Gross, nbest=1, method='adjr2')

library(MASS)
step <- stepAIC(fit, direction="both")
step$anova # display results

subsets <- regsubsets(Gross~., df_cat_filtered)

plot(subsets)
summary(subsets)

fit <- lm(Gross~., df_cat)
s <- step(fit)

lmp_cat <- run_rfe(x, y)

lmp_cat <- run_rfe(filter_columns(df_cat, c(n, 'Gross')), df_cat$Gross)
pricat(lmp_cat)
pred_cat <- predictors(lmp_cat)

head(lmProfile$resample)
plot(lmProfile)

evaluate_model_range('Gross ~ `RatedPG-13` + RatedPG + `ProductionWarner Bros. Pictures` + 
    `ProductionUniversal Pictures` + Genre_Drama + Genre_Action + 
    Genre_Adventure + Genre_Thriller + Genre_Fantasy + Language_French + 
    Country_USA + Country_Canada + Country_France + Nominations', df_cat_filtered)

```

```{r}
df_all <- cbind(subset(df_cat_filtered, select=-Gross), df_nt)
df_all_filtered <- filter_near_zero_var(df_all)
df_all_filtered <- filter_high_cor(df_all_filtered)
fit <- lm(Gross~., df_all_filtered)

step <- stepAIC(fit, direction="both")
step$anova # display results

evaluate_model_range('Gross ~ RatedR + `RatedPG-13` + `ProductionWarner Bros. Pictures` + 
    Genre_Drama + Genre_Action + Genre_Adventure + Genre_Horror + 
    Genre_Mystery + Country_UK + Country_Germany + imdbVotes + 
    tomatoUserReviews + Budget + Year_bin + tomatoUserReviews_bin', df_all_filtered)

df_final <- subset(df_all_filtered, select=c(Gross, RatedR, `RatedPG-13`, `ProductionWarner Bros. Pictures`, Genre_Drama, Genre_Action, Genre_Adventure, Genre_Horror, Genre_Mystery, Country_UK, Country_Germany, imdbVotes, tomatoUserReviews, Budget, Year_bin, tomatoUserReviews_bin))
```

```{r}
fit <- lm(Gross~.^2, df_final)
step <- stepAIC(fit, direction="both")
step$anova # display results
evaluate_model_range('Gross ~ RatedR + `RatedPG-13` + `ProductionWarner Bros. Pictures` + 
    Genre_Drama + Genre_Action + Genre_Adventure + Genre_Horror + 
    Genre_Mystery + Country_UK + Country_Germany + imdbVotes + 
    tomatoUserReviews + Budget + Year_bin + tomatoUserReviews_bin + 
    RatedR:Genre_Drama + RatedR:Genre_Action + RatedR:Genre_Adventure + 
    RatedR:Genre_Horror + RatedR:imdbVotes + RatedR:Budget + 
    RatedR:Year_bin + `RatedPG-13`:`ProductionWarner Bros. Pictures` + 
    `RatedPG-13`:Genre_Drama + `RatedPG-13`:Genre_Action + `RatedPG-13`:Genre_Horror + 
    `RatedPG-13`:imdbVotes + `RatedPG-13`:tomatoUserReviews + 
    `RatedPG-13`:Budget + `RatedPG-13`:Year_bin + `RatedPG-13`:tomatoUserReviews_bin + 
    `ProductionWarner Bros. Pictures`:Genre_Drama + `ProductionWarner Bros. Pictures`:Genre_Action + 
    `ProductionWarner Bros. Pictures`:Genre_Mystery + `ProductionWarner Bros. Pictures`:Country_UK + 
    `ProductionWarner Bros. Pictures`:Country_Germany + `ProductionWarner Bros. Pictures`:tomatoUserReviews + 
    `ProductionWarner Bros. Pictures`:Budget + `ProductionWarner Bros. Pictures`:Year_bin + 
    `ProductionWarner Bros. Pictures`:tomatoUserReviews_bin + 
    Genre_Drama:Genre_Adventure + Genre_Drama:Budget + Genre_Drama:Year_bin + 
    Genre_Action:Genre_Adventure + Genre_Action:Country_UK + 
    Genre_Action:imdbVotes + Genre_Action:tomatoUserReviews + 
    Genre_Action:Budget + Genre_Action:Year_bin + Genre_Action:tomatoUserReviews_bin + 
    Genre_Adventure:tomatoUserReviews + Genre_Adventure:Budget + 
    Genre_Horror:Budget + Genre_Mystery:imdbVotes + Country_UK:imdbVotes + 
    Country_UK:tomatoUserReviews_bin + Country_Germany:tomatoUserReviews + 
    imdbVotes:Year_bin + imdbVotes:tomatoUserReviews_bin + tomatoUserReviews:Year_bin + 
    tomatoUserReviews:tomatoUserReviews_bin + Budget:Year_bin + 
    Budget:tomatoUserReviews_bin', df_final)
```


**Q**: Explain what new features you designed and why you chose them.

**A**: 
