---
title: 'Project 2: Modeling and Evaluation'
subtitle: 'GID: mmendiola3'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
options(warn=-1) 
```

# Data

We will use the same dataset as Project 1: [`movies_merged`](https://s3.amazonaws.com/content.udacity-data.com/courses/gt-cs6242/project/movies_merged).

# Objective

Your goal in this project is to build a linear regression model that can predict the `Gross` revenue earned by a movie based on other variables. You may use R packages to fit and evaluate a regression model (no need to implement regression yourself). Please stick to linear regression, however.

# Instructions

You should be familiar with using an [RMarkdown](http://rmarkdown.rstudio.com) Notebook by now. Remember that you have to open it in RStudio, and you can run code chunks by pressing *Cmd+Shift+Enter*.

Please complete the tasks below and submit this R Markdown file (as **pr2.Rmd**) containing all completed code chunks and written responses, as well as a PDF export of it (as **pr2.pdf**) which should include all of that plus output, plots and written responses for each task.

_Note that **Setup** and **Data Preprocessing** steps do not carry any points, however, they need to be completed as instructed in order to get meaningful results._

# Setup

Same as Project 1, load the dataset into memory:

```{r}
load('movies_merged')
```

This creates an object of the same name (`movies_merged`). For convenience, you can copy it to `df` and start using it:

```{r}
df = movies_merged
cat("Dataset has", dim(df)[1], "rows and", dim(df)[2], "columns", end="\n", file="")
colnames(df)
```

## Load R packages

Load any R packages that you will need to use. You can come back to this chunk, edit it and re-run to load any additional packages later.

```{r}
suppressMessages(library(ggplot2))
suppressMessages(library(GGally))
suppressMessages(library(reshape2))
suppressMessages(library(caret))
suppressMessages(library(plyr))
suppressMessages(library(dplyr))
suppressMessages(library(splitstackshape))
suppressMessages(library(stringr))
suppressMessages(library(MASS))
suppressMessages(library(doParallel))
suppressMessages(library(rbenchmark))
```

```{r}
# Setup parallel processing
cl <- makeCluster(detectCores()-2)
registerDoParallel(cl)  
```

If you are using any non-standard packages (ones that have not been discussed in class or explicitly allowed for this project), please mention them below. Include any special instructions if they cannot be installed using the regular `install.packages('<pkg name>')` command.

**Non-standard packages used**:

    reshape2
    caret
    MASS
    plyr
    dplyr
    splitstackshape
    stringr
    doParallel
    rbenchmark

# Data Preprocessing

Before we start building models, we should clean up the dataset and perform any preprocessing steps that may be necessary. Some of these steps can be copied in from your Project 1 solution. It may be helpful to print the dimensions of the resulting dataframe at each step.

## 1. Remove non-movie rows

```{r}
# TODO: Remove all rows from df that do not correspond to movies
df <- subset(df, Type == 'movie')
nrow(df)
```

## 2. Drop rows with missing `Gross` value

Since our goal is to model `Gross` revenue against other variables, rows that have missing `Gross` values are not useful to us.

```{r}
# TODO: Remove rows with missing Gross value
df <- subset(df, !is.na(Gross))
nrow(df)
```

## 3. Exclude movies released prior to 2000

Inflation and other global financial factors may affect the revenue earned by movies during certain periods of time. Taking that into account is out of scope for this project, so let's exclude all movies that were released prior to the year 2000 (you may use `Released`, `Date` or `Year` for this purpose).

```{r}
# TODO: Exclude movies released prior to 2000
df <- subset(df, Year >= 2000)
nrow(df)
```

## 4. Eliminate mismatched rows

_Note: You may compare the `Released` column (string representation of release date) with either `Year` or `Date` (numeric representation of the year) to find mismatches. The goal is to avoid removing more than 10% of the rows._

```{r}
# TODO: Remove mismatched rows
year_delta <- function(year_, date) {
  if (is.na(year_) || is.na(date)) {
    return(0)
  } else if (year_ == as.numeric(format(date, "%Y"))) {
    return(0)
  }
  date = as.Date(date)
  year_start = as.Date(ISOdate(year_, 1, 1))
  year_end = as.Date(ISOdate(year_, 12, 31))
  diff = min(abs(c(date - year_start, date - year_end)))
  return(diff)
}

df$DaysDiff = mapply(year_delta, df$Year, df$Released)

# Threshold of days between Release and Year
threshold = 90
df_dedupped <- subset(df, DaysDiff < threshold)
sprintf("percent of rows removed: %f", 100 * (1 - (nrow(df_dedupped) / nrow(df))))

# Commit changes to df
df_before_dedup <- cbind(df)
df <- df_dedupped
```

## 5. Drop `Domestic_Gross` column

`Domestic_Gross` is basically the amount of revenue a movie earned within the US. Understandably, it is very highly correlated with `Gross` and is in fact equal to it for movies that were not released globally. Hence, it should be removed for modeling purposes.

```{r}
# TODO: Exclude the `Domestic_Gross` column
df <- subset(df, select=-Domestic_Gross)
```

## 6. Process `Runtime` column

```{r}
# TODO: Replace df$Runtime with a numeric column containing the runtime in minutes
parseRuntime <- function(string) {
  parts = unlist(strsplit(string, ' '))
  if (length(parts) == 2) {
    return(as.numeric(parts[1]))
  } else if (length(parts) == 4) {
    return(as.numeric(parts[1]) * 60 + as.numeric(parts[3]))
  } else {
    return(NA)
  }
}

df$Runtime = sapply(df$Runtime, parseRuntime)
```

Perform any additional preprocessing steps that you find necessary, such as dealing with missing values or highly correlated columns (feel free to add more code chunks, markdown blocks and plots here as necessary).

```{r}
# TODO(optional): Additional preprocessing
# Generate month feature to replace Released
df$Month = as.numeric(format(df$Released, "%m"))

# Convert Metascore to num
df$Metascore <- as.numeric(df$Metascore)

# Remove featues with clearly no correlation with Gross
df <- subset(df, select=-c(Date, Released, Poster, imdbID, Type, tomatoImage, tomatoURL, BoxOffice, Website, Response, DaysDiff))

# Filter major outliers
df <- subset(df, Gross < 2e9)
df <- subset(df, Gross > 1000)

# Clean column names
colnames(df) <- make.names(colnames(df), unique=T)

# Remove features with more than 10% NAs
pMiss <- function(x){round(sum(is.na(x))/length(x)*100)}
mc <- apply(df, 2, pMiss)
mc[mc>0]
columns_to_keep <- names(mc[mc < 10])
df <- subset(df, select=columns_to_keep)

# Remove high correlation features
df_numeric <- df[, sapply(df, is.numeric)]
cor_matrix <- cor(subset(df_numeric, select=-Gross), use='pairwise.complete.obs')
colnames(cor_matrix[, findCorrelation(cor_matrix, cutoff=0.75)])
df <- subset(df, select=-c(tomatoUserMeter, tomatoUserRating))

# Remove samples with NAs
df <- df[complete.cases(df), ]
```

_**Note**: Do NOT convert categorical variables (like `Genre`) into binary columns yet. You will do that later as part of a model improvement task._

## Final preprocessed dataset

Report the dimensions of the preprocessed dataset you will be using for modeling and evaluation, and print all the final column names. (Again, `Domestic_Gross` should not be in this list!)

```{r}
# TODO: Print the dimensions of the final preprocessed dataset and column names
dim(df)
colnames(df)
```

# Evaluation Strategy

In each of the tasks described in the next section, you will build a regression model. In order to compare their performance, use the following evaluation procedure every time:

1. Randomly divide the rows into two sets of sizes 5% and 95%.
2. Use the first set for training and the second for testing.
3. Compute the Root Mean Squared Error (RMSE) on the train and test sets.
4. Repeat the above data partition and model training and evaluation 10 times and average the RMSE results so the results stabilize.
5. Repeat the above steps for different proportions of train and test sizes: 10%-90%, 15%-85%, ..., 95%-5% (total 19 splits including the initial 5%-95%).
6. Generate a graph of the averaged train and test RMSE as a function of the train set size (%).

You can define a helper function that applies this procedure to a given model and reuse it.

```{r}

# Plot RMSE over various training sizes
plot_sub_data <- function(df, title, data_type) {
  df <- melt(df, id.vars='train_size', measure.vars=c('train', 'test'))
  return(ggplot(df, aes(train_size, value, color=variable)) +
    geom_line() +
    geom_point() +
    ggtitle(title) +
    labs(x='Train size (ratio of original data)', y=data_type))
}

# Split data into train and test sets
split_data <- function(df, train_ratio=0.8) {
  train_indicies<- sample(1:nrow(df), floor(train_ratio * nrow(df)))
  return(list(train=df[train_indicies,], test=df[-train_indicies,]))
}

# Fit a model with a random train/test sample and return RMSE for both sets
test_model <-function (formula, df, train_ratio=0.8, y_label='Gross') {
  df_sample <- split_data(df, train_ratio)
  model <- lm(formula, df_sample$train)
  suppressWarnings(test_residuals <- df_sample$test[, y_label] - predict(model, df_sample$test))
  result <- list(train=sqrt(mean(model$residuals^2)),
                 test=sqrt(mean(test_residuals^2)))
  return(result)
}

# Caculate the average RMSE over a number of trials for a given formula, data, and train/test split
evaluate_model <- function(formula, df, train_ratio=0.95, y_label='Gross', trials=10) {
  result <- foreach(i=1:trials, .combine=rbind, .export=c('test_model', 'split_data')) %dopar% {
    as.data.frame(test_model(formula, df, train_ratio=train_ratio, y_label=y_label))
  }
  return(list(
            train=mean(result$train),
            test=mean(result$test)
         ))
}

# Evaluate performance of a model over a range of train/test set sizes
evaluate_model_range <- function(formula, df, y_label='Gross', trials=50, max_time=20) {
  sample_sizes <- seq(0.05, 0.95, 0.05)
  duration <- system.time(evaluate_model(formula, df, trials=detectCores()))[3]
  trials_till_max_time <- ceiling(max_time * 4/ (duration * length(sample_sizes)))
  trials <- min(trials, trials_till_max_time)
  print(paste(trials, 'trials'))
  rmse <- data.frame()
  for (i in sample_sizes) {
    rmse <- rbind(rmse, c(evaluate_model(formula, df, i, y_label, trials), train_size=i))
  }
  return(list(rmse=rmse, plot=plot_sub_data(rmse, 'RMSE vs. Training size', 'RMSE')))
}

# Run a t-test on the set of RMSEs observed over a number of trials for two different models
evaluate_model_change <- function(formula1, df1, formula2, df2, train_ratio=0.95, y_label='Gross', trials=100, max_time=20) {
  duration <- system.time(evaluate_model(formula1, df1, trials=detectCores()))[3]
  duration <- duration + system.time(evaluate_model(formula2, df2, trials=detectCores()))[3]
  trials_till_max_time <- ceiling(max_time * 4/ duration)
  trials <- min(trials, trials_till_max_time)
  print(paste(trials, 'trials'))
  m1 <- foreach(i=1:trials, .combine=rbind, .export=c('test_model', 'split_data')) %dopar% {
    as.data.frame(test_model(formula1, df1, train_ratio=train_ratio, y_label=y_label))
  }
  m2 <- foreach(i=1:trials, .combine=rbind, .export=c('test_model', 'split_data')) %dopar% {
    as.data.frame(test_model(formula2, df2, train_ratio=train_ratio, y_label=y_label))
  }
  return(list(train=t.test(m1$train, m2$train, alternative='greater'),
              test=t.test(m1$test, m2$test, alternative='greater')))
}
```

```{r}
# Run benchmark on random data
df_random <- data.frame(x=runif(nrow(df)), Gross=df$Gross)
evaluate_model_range(Gross~., df_random)
evaluate_model_change(Gross~., df_random, Gross~.^2, df_random, trials=500)
```

# Tasks

Each of the following tasks is worth 20 points. Remember to build each model as specified, evaluate it using the strategy outlined above, and plot the training and test errors by training set size (%).

## 1. Numeric variables

Use linear regression to predict `Gross` based on all available _numeric_ variables.

```{r}
# TODO: Build & evaluate model 1 (numeric variables only)
df_numeric <- df[, sapply(df, is.numeric)]
names(df_numeric)
```

```{r}
evaluate_model_range('Gross~.', df_numeric, 'Gross')
```

**Q**: List all the numeric variables you used.

**A**:

[1] "Year"              "Runtime"           "Metascore"         "imdbRating"        "imdbVotes"        
 [6] "tomatoMeter"       "tomatoRating"      "tomatoReviews"     "tomatoFresh"       "tomatoRotten"     
[11] "tomatoUserReviews" "Budget"            "Month"          


The resulting model produced an RMSE of ~1e8 for both training and test samples.


## 2. Feature transformations

Try to improve the prediction quality from **Task 1** as much as possible by adding feature transformations of the numeric variables. Explore both numeric transformations such as power transforms and non-numeric transformations of the numeric variables like binning (e.g. `is_budget_greater_than_3M`).

### Setup functions
These help to evaluate numeric and non-numeric transformations

```{r}
# TODO: Build & evaluate model 2 (transformed numeric variables only)

df_nt <- cbind(df_numeric)

# Generate a set of models based on a set of independent var transformations
reg_transforms <- function(x, y) {
  return(list(
    linear = lm(y~x),
    log = lm(y~log(x+1)),
    quad = lm(y~I(x^2)),
    cubic = lm(y~I(x^3)),
    quartic = lm(y~I(x^4)),
    quintic = lm(y~I(x^5)),
    reciprocal = lm(y~1/(x+1))
  ))
}

get_r2 <- function(fit) {
  return(summary(fit)$r.squared)
}

get_rmse <- function(fit) {
  return(sqrt(mean(fit$residuals^2)))
}

get_cor <- function(fit) {
  return(as.vector(cor(fit$model[1], fit$model[2])))
}

# Calculate model fit metrics for a given model
eval_fit <- function(fit) {
  return(data.frame(r2=get_r2(fit), rmse=get_rmse(fit), cor=get_cor(fit)))
}

# Calculate the optimum number of ntile bins for a given feature
best_bins <- function(x, y) {
  fit <- lm(y ~ x)
  result <- list(r2=summary(fit)$r.squared, bins=0)
  for (i in 1:200) {
    b <- ntile(x, i)
    fit <- lm(y ~ x + b)
    r2 <- summary(fit)$r.squared
    if (r2 > result$r2) {
      result$r2 <- r2
      result$bins <- i
    }
  }
  return(result)
}
```

### Visualize features
```{r}
for (feature in setdiff(names(df_nt), 'Gross')) {
  print(plot(df_nt[,feature], df_nt$Gross, main=feature))
}
```


### Evaluate numeric transformations

```{r}
for (feature in setdiff(names(df_numeric), 'Gross')) {
  print(feature)
  fits <- reg_transforms(df_numeric[, feature], df_numeric$Gross)
  perf <- sapply(fits, eval_fit)
  print(perf)
}
```

```{r}
# Numeric transformations
df_nt$Runtime_cubic <- df_nt$Runtime^3
df_nt$imdbRating_power <- df_nt$imdbRating^11
df_nt$tomatoReviews_cubic <- df_nt$tomatoReviews^3
df_nt$tomatoFresh_quad <- df_nt$tomatoFresh^2
df_nt$tomatoRotten_quant <- df_nt$tomatoRotten^4
df_nt$tomatoMonth_log <- log(df_nt$Month)
```


### Evaluate binning of numeric features
```{r}
# Binning transformations

for (feature in setdiff(names(df_numeric), 'Gross')) {
  b <- best_bins(df_numeric[, feature], df_numeric$Gross)
  if (b$bins > 0) {
    print(cbind(b, name=feature))
    df_nt[, paste(feature, '_bin', sep='')] <- ntile(df_numeric[, feature], b$bins)
  }
}

```

```{r}
evaluate_model_change('Gross~.', df_numeric, 'Gross~.', df_nt)
evaluate_model_range('Gross~.', df_nt)
```


**Q**: Explain which transformations you used and why you chose them.

**A**: 

Each feature was evaluted for a number of different numeric transforms:

    linear = lm(y~x),
    log = lm(y~log(x+1)),
    quad = lm(y~I(x^2)),
    cubic = lm(y~I(x^3)),
    quartic = lm(y~I(x^4)),
    quintic = lm(y~I(x^5)),
    reciprocal = lm(y~1/(x+1))
    
A model was built with each transformation and the resulting R^2, RMSE, and correlation coefficient was inspected. For each feature, the model fit metrics were inspected before and after applying each of these transformations. Based on the results, the following numeric transformation features were added:

    Runtime^3
    imdbRating^11
    tomatoReviews^3
    tomatoFresh^2
    tomatoRotten^4
    log(Month)

Binning was also evaluated for each feature by splitting the data points into equal sized bins. Bin counts between 1 and 200 were tested and the bin count that resulted in the highest r^2 model was chosen. The following bin features where added:

    bins 15         "Year"
    bins 8         "Runtime"
    bins 17         "Metascore"
    bins 27         "imdbRating"
    bins 8         "imdbVotes"
    bins 86        "tomatoMeter"
    bins 23         "tomatoRating"
    bins 35        "tomatoReviews"
    bins 17        "tomatoFresh"
    bins 18         "tomatoRotten"
    bins 27        "tomatoUserReviews"
    bins 29        "Budget"
    bins 2          "Month"

The final result of these transformations was an improvement of about 5% on the test RMSE on the training and test sets (~9.5e7). The t-test between the RMSE mean across trials for the numeric model verses the tranformed model shows a p-value of 0.01. This indicates the model improvement is statistically significant.

## 3. Non-numeric variables

Write code that converts genre, actors, directors, and other categorical variables to columns that can be used for regression (e.g. binary columns as you did in Project 1). Also process variables such as awards into more useful columns (again, like you did in Project 1). Now use these converted columns only to build your next model.

```{r}
# TODO: Build & evaluate model 3 (converted non-numeric variables only)

# Create a non-numeric dataframe to work with
df_cat <- df[, sapply(df, function(x) !is.numeric(x))]
df_cat$Gross <- df$Gross

# Filter non-catagorical features
df_cat <- subset(df_cat, select=-c(DVD, Title, tomatoConsensus, Plot))

filter_columns <- function(df, column_names) {
  if (length(column_names) > 0) {
    filtered <- which(names(df) %in% column_names)
    if (length(filtered) > 0) {
      return(df[, -filtered])
    }
  }
  return(df)
}

# Converts the top N unique values to binary features
factor_to_features <- function(df, feature, top=10, append=TRUE) {
  df_factor <- subset(df, select=feature)
  df_features <- model.matrix(~., df_factor)[,-1]
  if (top > 0) {
    sums <- colSums(df_features)
    top_features = names(sort(sums, decreasing = TRUE)[1:min(top, length(sums))])
    df_features <- subset(df_features, select=top_features)
  }
  if (append) {
    df <- cbind(df, df_features)
  } else {
    df <- df_features
  }
  df <- filter_columns(df, c(feature, '(Intercept)'))
  colnames(df) <- make.names(colnames(df), unique=T)
  return(df)
}

# Converts the top N unique values to binary features. Assumes comma seperated values in original feature.
string_to_features <- function(df, feature, top=10, append=TRUE) {
  df_sub <- subset(df, select=feature)
  df_sub <- cSplit_e(df_sub, feature, sep=',', mode='binary', type='character', fill=0, drop=TRUE)
  if (top > 0) {
    sums <- colSums(df_sub)
    top_features = names(sort(sums, decreasing = TRUE)[1:min(top, ncol(df_sub))])
    df_sub <- subset(df_sub, select=top_features)
  }
  if (append) {
    df <- cbind(df, df_sub)
  } else {
    df <- df_sub
  }
  df <- filter_columns(df, c(feature, 'na'))
  colnames(df) <- make.names(colnames(df), unique=T)
  return(df)
}

# Removes comments inside ()
clean_writer_strings <- function(string_) {
  return(str_replace_all(string_, ' *\\([^\\)]*\\)', ''))
}

# Clean 'Writer'
df_cat$Writer <- sapply(df_cat$Writer, clean_writer_strings)
```

```{r}
# Create binary features for: 'Rated', 'Production'
for (feature in c('Rated', 'Production')) {
  df_cat <- factor_to_features(df_cat, feature)
}

# Create binary features for: 'Genre', 'Director', 'Writer', 'Actors', 'Language', 'Country'
for (feature in c('Genre', 'Director', 'Writer', 'Actors', 'Language', 'Country')) {
  df_cat = string_to_features(df_cat, feature)
}

# Clean columns
df_cat[c('Writer', 'na', 'Writer_N/A')] = NULL

# Parse Awards
parse_awards <- function(msg, patterns) {
  if (is.na(msg)) {
    return(NA)
  }
  msg = tolower(msg)
  value = 0
  for (pattern in patterns) {
    m = str_match(msg, pattern)[1, 2]
    if (!is.na(m)) {
      value = value + as.integer(m)
    }
  }
  return(value)
}

# Convert Awards feature to Wins and Nominations features
awards_patterns = c('won (\\d+)', "(\\d+) win")
nomination_patterns = c('nominated for (\\d+)', "(\\d+) nomination")
df_cat$Wins = sapply(df_cat$Awards, parse_awards, pattern=awards_patterns)
df_cat$Nominations = sapply(df_cat$Awards, parse_awards, pattern=nomination_patterns)
df_cat['Awards'] = NULL
```

```{r}
# Evaluate the non-numeric only model
evaluate_model('Gross~.', df_cat)
evaluate_model_range('Gross~.', df_cat)
```

**Q**: Explain which categorical variables you used, and how you encoded them into features.

**A**: 

I used the following original features:

  'Rated', 'Production' 'Genre', 'Director', 'Writer', 'Actors', 'Language', 'Country' 'Awards'
  
Rated and Production were converted by taking the set of unique values and making each a seperate binary feature. These features were then reduced to the top ten most common.

The remaining features, besides Awards, were converted by parsing the string as comma seperated values and creating binary features from each of the unique extracted values. As before, only the top ten most common derived features were retained.

The Awards feature extraction uses regex parsing to pull out the number of wins and nominations. Wins and Nominations features replace Awards.

The resulting non-numeric only model resulted in an RMSE of ~1.4e8 for train and test samples.


## 4. Numeric and categorical variables

Try to improve the prediction quality as much as possible by using both numeric and non-numeric variables from **Tasks 2 & 3**.

```{r}
# TODO: Build & evaluate model 4 (numeric & converted non-numeric variables)

# Combine numeric and non-numeric features
df_all <- merge(df_nt, df_cat)
```

```{r}
evaluate_model_change('Gross~.', df_nt, 'Gross~.', df_all)
evaluate_model_change('Gross~.', df_cat, 'Gross~.', df_all)
evaluate_model_range('Gross~.', df_all, max_time=120)
```

The combined model, with numeric and non-numeric featues, performed significantly beter than the catagory only model and was about the same as the numeric only model. The best RMSE on the test set was 9.5e7. RMSE on the training set (95%) was better on the mixed model. Since the mixed model did not improve over the numeric model, the next step is to do some feature selection. We already know that the mixed model is performing similar to a model with less features, so there should be some features that are not contributing.


```{r results='hide', message=FALSE, warning=FALSE}
# Filter features with high correlation with other features
filter_high_cor <- function(df, cutoff=0.75) {
  if ('Gross' %in% colnames(df)) {
    x <- subset(df, select=-Gross)
  }
  cor_matrix <- cor(x, use='pairwise.complete.obs')
  high_cor <- findCorrelation(cor_matrix, cutoff=cutoff, names=TRUE)
  return(filter_columns(df, high_cor))
}

# Filter features with near zero variance
filter_near_zero_var <- function(df) {
  near_zero_var_columns <- names(df)[nearZeroVar(df)]
  return(filter_columns(df, near_zero_var_columns))
}

build_formula <- function(features) {
  return(paste('Gross ~', paste(features, collapse='+')))
}

# Perform univariate feature filtering
run_sbf <- function(formula, df) {
  ctrl <- sbfControl(functions = lmSBF,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = TRUE, saveDetails=T)
  return(sbf(form=formula,
             data=df,
             sbfControl = ctrl))
}

# Filter features
lmp_all <- run_sbf(Gross~., df_all)
df_filtered <- lmp_all$fit$model
colnames(df_filtered)[1] <- 'Gross'
```

```{r}
paste('Keeping', ncol(df_filtered), 'out of', ncol(df_all), 'features')
evaluate_model_change('Gross~.', df_all, 'Gross~.', df_filtered)
evaluate_model_range('Gross~.', df_filtered)
```

Using univariate feature filtering on the full set of features (112 features) produced a simplified model with 78 features. RMSE on the simplified model improved slightly to 9.1e7 on the test set.

## 5. Additional features

Now try creating additional features such as interactions (e.g. `is_genre_comedy` x `is_budget_greater_than_3M`) or deeper analysis of complex variables (e.g. text analysis of full-text columns like `Plot`).

```{r}
# TODO: Build & evaluate model 5 (numeric, non-numeric and additional features)

search_colnames <- function(term, df) {
  return(colnames(df)[which(str_detect(colnames(df), term))])
}

build_formula_by_term <- function(term, df) {
  return(paste(search_colnames(term, df_filtered), collapse='+'))
}
```

### Interactions

***Genre interactions***
```{r}
formula <- paste('Gross~(', build_formula_by_term('Genre', df_filtered), ')^2+.')
evaluate_model_change(Gross~., df_filtered, formula, df_filtered)
```

***Actor interactions***
```{r}
formula <- paste('Gross~(', build_formula_by_term('Actor', df_filtered), ')^2+.')
evaluate_model_change(Gross~., df_filtered, formula, df_filtered)
```

***Writer interactions***
```{r}
formula <- paste('Gross~(', build_formula_by_term('Writer', df_filtered), ')^2+.')
evaluate_model_change(Gross~., df_filtered, formula, df_filtered)
```

***Budget, Year, Runtime interaction***
```{r}
evaluate_model_change(Gross~., df_filtered, Gross~(Budget_bin+Year_bin+Runtime_bin)^2+., df_filtered)
```


### Production staff counts and description lengths
```{r}
# Try engineering new features

count_entries <- function(column) {
  return(str_count(column, ',') + 1)
}

# Try entity counts
count_features <- c('Genre', 'Director', 'Writer', 'Actors', 'Language', 'Country')
df_count <- as.data.frame(sapply(df[, count_features], count_entries))
colnames(df_count) <- sapply(colnames(df_count), function(n) return(paste('Count', n)))
evaluate_model_change(Gross~., df_filtered, Gross~., cbind(df_filtered, df_count))

# Try string lengths
length_features <- c('Title', 'Plot', 'tomatoConsensus')
df_length <- as.data.frame(sapply(df[, length_features], str_length))
colnames(df_length) <- sapply(colnames(df_length), function(n) return(paste('Length', n)))
evaluate_model_change(Gross~., df_filtered, Gross~., cbind(df_filtered, df_length))
```


### Ordered Rating scale
```{r}
# Try Rated scale
rate_scale <- function(rating) {
  ratings <- c('G', 'PG', 'PG-13', 'R', 'NC-17')
  if (rating %in% ratings) {
    return(which(ratings == rating))
  } else {
    return(6)
  }
}

df_rating <- cbind(df_filtered)
df_rating$rate_scale <- sapply(df$Rated, rate_scale)
evaluate_model_change(Gross~., df_filtered, Gross~., df_rating)
evaluate_model_range(Gross~., df_rating)
```

### Count of top Actors, Writers, Languages, Countries, Directors, and Production studios.
```{r}
# Try top count
df_top <- cbind(df_filtered)
df_top$top_actor_count <- rowSums(string_to_features(df, 'Actors', top=10, append=F))
df_top$top_writer_count <- rowSums(string_to_features(df, 'Writer', top=100, append=F))
df_top$top_language_count <- rowSums(string_to_features(df, 'Language', top=10, append=F))
df_top$top_country_count <- rowSums(string_to_features(df, 'Country', top=5, append=F))
df_top$top_director <- rowSums(factor_to_features(df, 'Director', top=100, append=F))
df_top$top_production <- rowSums(factor_to_features(df, 'Production', top=10, append=F))

evaluate_model_change(Gross~., df_filtered, Gross~., df_top)
# evaluate_model(Gross~.^2, df_top)
```
### Genre featues reintroduced

```{r}
df_genre <- string_to_features(df, 'Genre', top=100, append=F)
df_genre_eval <- merge(df_filtered, df_genre)
evaluate_model_change(Gross~., df_filtered, Gross~., df_genre_eval, trials=10, max_time=120)
evaluate_model_range(Gross~., df_genre_eval, trials=10, max_time=3000)
```


**Q**: Explain what new features you designed and why you chose them.

**A**: 

A number of interaction models were evaluated, mixes of Genres, Actors, and Writers. The intuition was that movies with a mix of specific sets of Actors, Writers, or Genres might do beter than others. A custum pairwise interaction with Budget_bin, Year_bin, and Runtime_bin was also attempted to explore the possible relationships of Budget and Runtime over the years. While some of these models improved RMSE on the training set, none of them made a significant improvement on the test set.

New features were created on character data indicating the number of elements (comma seperated values) and field lengths. This indicates the number of Writers, Directors, etc. that were invovled in a movie. The length transformation also indicates how much was written in the Plot and tomatoConsensus fields. Unfortunately, none of these new features contributed significantly to improving the model.

A feature was created to capture ordering in the Rated feature as a numeric value, with G being the lowest and increasing from there. This new feature did not significantly improve the model either.

Yet another feature was added that indicated the quantity of top N Actors, etc. that were associated with each movie. As an example, a movie could have 3 of the top 10 most prolific writers. This was calculated for Actors, Writers, Languages, Countries, Directors, and Production studios. Again, these new features did not improve the model performance.

The final attempt was to reintroduce features that where previously filtered to reduce dementionality. In this final model, all Genres were captured in binary featues instead of limiting it to the top 10. The resulting model was able to reduce the test set RMSE to around 8.2e7. This leads to the belief that there are likely other predictive features in the dataset that would be discovered with an exhaustive, and potentially computationally costly, search. An effort was put into exploring recursive feature selection, but was abandoned in light of the computational time required given the number of features available.